\documentclass{article}
\usepackage{booktabs}
\usepackage{ctex}
\author{SwitZ \and Shichien \and Kylin-OIO}
\title{Write Anything Here}
\begin{document}
\maketitle
\section{Porter Robinson Discography}
\subsection{Worlds(2014)}
\begin{itemize}
    \item Divinity(feat. Amy Millan)
    \item Sad Machine
    \item Years of War(feat. Breanne Duren and Sean Caskey)
    \item Flicker
    \item Fresh Static Snow
    \item Hollowheart(2024)(feat. Amy Millan)
    \item Polygon Dust(feat. Lemaitre)
    \item Hear the Bells(feat. Imaginary Cities)
    \item Natural Light
    \item Lionhearted(feat. Urban Cone)
    \item Sea of Voices
    \item Fellow Feeling
    \item Goodbye to a World
    \item Shepherdess/She Heals Everything(2021)
\end{itemize}
\subsection{Nurture(2021)}
\begin{itemize}
    \item Lifelike
    \item Look at the Sky
    \item Get Your Wish
    \item Wind Tempos
    \item Musician
    \item Do-re-mi-fa-so-la-ti-do
    \item Mother
    \item Dullscythe
    \item Sweet Time
    \item Mirror
    \item Something Comforting
    \item Blossom
    \item Unfold(feat. Totally Enormous Extinct Dinosaurs)
    \item Trying to Feel Alive
    \item Fullmoon Lullaby(feat. Wednesday Campanella)
\end{itemize}
\subsection{SMILE!:D(2024)}
\begin{itemize}
    \item Knock Yourself Out XD
    \item Cheerleader
    \item Russian Roulette
    \item Perfect Pinterest Garden
    \item Year of the Cup
    \item Kistune Maison Freestyle
    \item Easier to Love You
    \item Mona Lisa
    \item Is There Really No Happiness?
    \item Everthing to Me
\end{itemize}

    \section{冲突示例}

    我是来捣蛋的。

    \section{ Switz 的表格}
    \begin{table}[h]
        \centering
        \begin{tabular}{lcr}
            \toprule
            \textbf{Column 1} & \textbf{Column 2} & \textbf{Column 3} \\
            \midrule
            \textit{Left-aligned text} & \textit{Centered text} & \textit{Right-aligned text} \\
            \texttt{Another left-aligned text} & \texttt{Another centered text} & \texttt{Another right-aligned text} \\
            \bottomrule
        \end{tabular}
        \caption{SwitZ 的表格}
        \label{tab:switz}
    \end{table}
    如表~\ref{tab:switz}所示，这是SwitZ的表格。
    \section{ Kylin-OIO 的表格}
    \begin{table}[h]
        \centering
        \begin{tabular}{l c r} 
            \toprule
          \textbf{Column 1} & \textbf{Column 2} & \textbf{Column 3} \\
          \midrule
           \textit{Left aligned text}  & \textit{Centered text} & \textit{Right aligned text} \\
           \texttt{Another left aligned text} & \texttt{Another centered text} & \texttt{Another right aligned text}\\
           \bottomrule
        \end{tabular}
        \caption{三线表示例}
        \label{tab:my_table}
    \end{table}
    
    如\ref{tab:my_table} 所示，第三行第三列已改为代码字体。
\end{document}  
